---
title: "Project: "
author: "Michil Trofimov, Vlada Tuliavko, Ustin Zolotikov"
date: "2023-01-16"
#bibliography: packages.bib
output: 
  html_document:
    latex_engine : xelatex
    df_print: default
    highlight: zenburn
    toc: TRUE
    toc_depth: 3
mainfont : NanumGothic    
editor_options: 
  markdown: 
    wrap: 72
---

## Dependencies

Libraries that we have used. Data.table, dlookr, flextable were not reviewed in our lecture.

```{r setup, message=FALSE}
library(data.table)
library(ggplot2)
library(dplyr)
library(dlookr)
library(flextable)
```

```{r upload data, include=FALSE}
setwd('/Users/m.trofimov/Dropbox/Study/BI/R_statistics/R_project_1/data')
df = fread('day.csv', na.strings = c('',NA))
```

## Pre-process

Let's look at our data with a function `diagnose` from a package
*dlookr*

```{r, echo=FALSE}
diagnose(df) %>% flextable()
```

We need to factories data related to the date (season, yr, mnth, holiday, weekday, workingday) and variable weathersit (type of weather).

There are missing values in columns temp, hum, windspeed and registered.
Considering that each value corresponds to a day of a year, we would not
like to drop rows with missing values.

Let's fill missing values:

-   temp: we will take values from column atemp
-   hum: we will fill with an average value of humidity in a
    corresponding month
-   windspeed: the same as hum
-   registered: we find value by counting cnt - casual

```{r fill_na, include=FALSE}
df = df %>% mutate(temp = coalesce(temp,atemp))
                   
mean_hum_windspeed = data.frame(df %>% group_by(mnth) %>% summarise(mean_hum = mean(hum, na.rm = T),
                                    mean_windspeed = mean(windspeed, na.rm = T)))

df_clean = df %>% mutate(
  hum = ifelse(
  (is.na(hum) & (mnth == 1)), mean_hum_windspeed[mean_hum_windspeed$mnth == 1,]$mean_hum, 
  ifelse(
    (is.na(hum) & (mnth == 6)), mean_hum_windspeed[mean_hum_windspeed$mnth == 6,]$mean_hum,
  ifelse(
    (is.na(hum) & (mnth == 12)), mean_hum_windspeed[mean_hum_windspeed$mnth == 12,]$mean_hum, as.double(hum)))),
  
  windspeed = ifelse(
  (is.na(windspeed) & (mnth == 11)), mean_hum_windspeed[mean_hum_windspeed$mnth == 11,]$mean_windspeed, 
  as.double(windspeed)),
  
  registered = ifelse(
    is.na(registered), 1985-186, as.double(registered)
  ))

```

```{r categorise variables, include=FALSE}
df_clean$mnth = as.factor(df_clean$mnth)
df_clean$season = as.factor(df_clean$season)
df_clean$yr = as.factor(df_clean$yr)
df_clean$holiday = as.factor(df_clean$holiday)
df_clean$weekday = as.factor(df_clean$weekday)
df_clean$workingday = as.factor(df_clean$workingday)
df_clean$weathersit = as.factor(df_clean$weathersit)
```

Now we need to find outliers


```{r, echo=FALSE}
diagnose_outlier(df_clean) %>% flextable()
```

```{r, include=FALSE}
find_outliers(df_clean, index = F)
```
```{r, echo=FALSE}
df_clean %>%
  select(hum, windspeed) %>%
  plot_outlier
```

There is a weird outlier for humidity with value 0. Remove it.

```{r, include=FALSE}
df_clean = df_clean %>%
  filter(hum != 0)
```



## Correlation plot

```{r, message=FALSE}
df_clean %>%
  correlate() %>%
  plot()
```
## Statistical analysis

### Linear regression

It would be interesting to check correlation between temp and number of users.

```{r}
plot(df_clean$temp, df_clean$cnt)
```

Does not look obvious. Let's fit linear regression number of users ~ temperature

```{r}
cnt_temp_lm_fit = lm(cnt ~ temp, df_clean)
plot(cnt_temp_lm_fit)
```

- Data is heteroscedastic, due to the fact that at small and large values residuals begin to deviate from 0.

- From q-q plot, we can see that residuals are normally distributed


```{r}
summary(cnt_temp_lm_fit)
```
There is very significant p-value < 2e-16, which indicates that there is a linear relationship between response variable (number of users) and predict variable (temperature)

### T-test

It would be interesting to see, whether day is a holiday or not influeneces number of users

```{r}
holiday_no = df_clean %>%
  filter(holiday == "0")

holiday_yes = df_clean %>%
  filter(holiday == "1")

t.test(holiday_no$cnt, holiday_yes$cnt)
```

There is no significant association (p-value > 0.05) between holiday and number of users.

Perhaps, the problem is in the size of samples. We have only 21 holiday days.

Let's check whether its a working day or not, influence number of users.

```{r}
weekdays = df_clean %>%
  filter(workingday == "1")

weekends = df_clean %>%
  filter(workingday == "0")

t.test(weekdays$cnt, weekends$cnt)
```

There is no significant association (p-value > 0.05) between holiday and number of users.

Let's look at number of unregistered users

```{r}
weekdays = df_clean %>%
  filter(workingday == "1")

weekends = df_clean %>%
  filter(workingday == "0")

t.test(weekdays$casual, weekends$casual)
```

Yes, there is significant association between working day or not and number of casual users